---
title: "Homework 5 "
output: github_document
---

```{r, setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in the data

```{r}
homicide_df = 
  read.csv("./homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Do a prop.test for a single city--Baltimore,

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_test = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_test) %>% 
  select(city_state, estimate, conf.low, conf.high)
```


```{r}
results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1)
  )
```


## Problem 2

combine csv files in to a data frame
```{r message=FALSE, warning=FALSE}
longstudy_df = 
  tibble(
    path = list.files("lda_data")
    ) %>% 
  mutate(
    path = str_c("lda_data/", path),
    data = map(.x = path, ~read_csv(.x)),
    path = str_remove(path, "lda_data/"),
    path = str_remove(path, ".csv")) %>% 
  unnest() %>% 
  separate(path, into = c("arm", "subject_id"),sep = "_") %>% 
  mutate(
    arm = ifelse(arm == "con", "Control", "Experiment")
  ) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week_number",
    values_to = "observations"
  )
```

Make a spaghetti plot

```{r}
longstudy_df %>% 
  unite("id", c(arm, subject_id), sep = "_", remove = F) %>% 
  ggplot(aes(x = week_number, y = observations, color = arm)) +
  geom_line(aes(group = as.factor(id)),alpha = .5) +
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1)
    )
```

From this spaghetti plot, we could see that experiment group and control group start from the close observation value. Then the general trend of experiment group is increasing, while control group seems like to remain unchanged. This comment only indicate the overall trend for each group as we can see that observations are oscillating over time for each subject.


## Problem 3

Build a function about how to calculate the estimate and p -value
```{r}
sim_t_test = function(n = 30, mu, sigma = 5, method = "two_sided") {
  sim_data = tibble(
    x = rerun(5000, rnorm(n, mean = mu, sd = sigma)))
  
  if (method == "two_sided") {
    
    t_critical = qt(0.975,29)
    
    sim_data %>% 
      mutate(
        t_test = map(.x = x, ~t.test(.x, mean = 0,
                                     paird = FALSE,conf.level = 0.95,
                                     alternative = "two.sided")),
        tidy_t_test = map(.x = t_test, ~broom::tidy(.x))) %>% 
      select(-t_test) %>% 
      unnest(tidy_t_test) %>% 
      select(estimate, p.value) %>% 
      mutate(
        accept_h0 = case_when(
          abs(estimate) > t_critical ~ "Reject",
          abs(estimate) <= t_critical ~ "Fail to reject"
        )
      )} 
  
  else if (method == "less") {
    t_critical = qt(0.05,29)
    
    sim_data %>% 
      mutate(
        t_test = map(.x = x, ~t.test(.x, mean = 0,
                                     paird = FALSE,conf.level = 0.95,
                                     alternative = "less")),
        tidy_t_test = map(.x = t_test, ~broom::tidy(.x))) %>% 
      select(-t_test) %>% 
      unnest(tidy_t_test) %>% 
      select(estimate, p.value) %>% 
      mutate(
        accept_h0_miu0 = case_when(
          abs(estimate) < t_critical ~ "Reject",
          abs(estimate) >= t_critical ~ "Fail to reject"
        )
      )
  }
    else if (method == "greater") {
    t_critical = qt(0.95,29)
    
    sim_data %>% 
      mutate(
        t_test = map(.x = x, ~t.test(.x, mean = 0,
                                     paird = FALSE,conf.level = 0.95,
                                     alternative = "greater")),
        tidy_t_test = map(.x = t_test, ~broom::tidy(.x))) %>% 
      select(-t_test) %>% 
      unnest(tidy_t_test) %>% 
      select(estimate, p.value) %>% 
      mutate(
        accept_h0_miu0 = case_when(
          abs(estimate) > t_critical ~ "Reject",
          abs(estimate) <= t_critical ~ "Fail to reject"
        )
      )
      }
}
```

for miu = 0, 1, 2, 3, 4, 5, 6
```{r}
set.seed(1)

clean_outp_test = 
  tibble(
    miu_value = c(0, 1, 2, 3, 4, 5, 6)) %>% 
    mutate(output_lists = map(.x = miu_value, ~sim_t_test(mu = .x))) %>% 
    unnest(output_lists)

clean_outp_test
   
```

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. 
```{r}
prop_pl =
  clean_outp_test %>% 
  group_by(miu_value) %>% 
  summarize(
    reject = sum(accept_h0 == "Reject"),
    total  = n()
  ) %>% 
  mutate(
    prop = map2(.x = reject, .y = total, ~prop.test(x = .x, n = .y)),
    tidy_test = map(.x = prop, ~broom::tidy(.x))
  ) %>% 
  select(-prop) %>% 
  unnest(tidy_test) %>% 
  select(miu_value, estimate, conf.low, conf.high)

prop_pl %>%
  mutate(
    miu_value = as.factor(miu_value)
  ) %>% 
  ggplot(aes(x = miu_value, y = estimate, fill = miu_value)) +
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  ggtitle("The proportion of times the null was rejected")
  ylab("estimate proportion")

```

From this plot, we could see that as the effect size of the difference between sample mean and hypothesis population mean  increases, the power of the test that rejects the null hypothesis is increasing